---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "sipreamble.tex"
bibliography: "references.bib"
title: "Paper title"
author:
  - Author 1^[Institution 1, email1]
  - Author 2^[Institution 2, email2]
---

```{r sisetup, echo=F}
options(tinytex.clean = FALSE)
```

# Supporting Information

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}


- Tables with data presented in figures 5 and 6
- Table with Tajima's D for syn, mis, lof mutations for all, within, or outside of domains

\clearpage
\newpage

# Supplementary Tables

```{r tabS1, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
pops <- read.csv("tables/populations.txt", sep=";", header=TRUE)
knitr::kable(pops, "latex", booktabs=T,
    caption="Thousand Genomes Project population descriptions for populations used in this study.") %>%
kable_styling(latex_options = "HOLD_position")
```


```{r tabS2, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
taj <- read.csv("tables/tajimas_d.txt", sep=";", header=TRUE)
knitr::kable(taj, "latex", booktabs=T, longtable=T,
    linesep = c("", "", "", "", "", "", "", "", "\\addlinespace"),
    caption="Tamija's $D$ for classes of coding mutations, both within annotated domains and outside of domains.") %>%
kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```



\clearpage
\newpage

# Supplementary Figures

1) Accuracy of jackknife for varying sample size
2) Repeat of figures 2, 3, and 4 but for average $D$ instead of $\sigma_d^2$
3) 

\clearpage
\newpage

# Supporting References
